---
title: "Graphical representation of oil consumption"
author: "Green orange"
date: "13 November 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(plotly)
library(tidyr)
library(xlsx)

```


## Short description
#### The following slide shows oil consumption per capita in tonnes per year for the following countries:


- China
- United States
- Germany
- Norway
- Venezuela

*The dataset contains the data from 1965 to 2010 and was compiled by BP (see [http://www.bp.com/statisticalreview](http://www.bp.com/statisticalreview) for details)*

## Plotly code chunk

The final command to make the plot using the R plotly package looks like this:
```{r plotly_code, eval=FALSE, echo = TRUE}
plot_ly(data = oil_country, x = ~year, y = ~oil.consumption,
        type = "scatter", mode = "lines+markers", color = ~country)
        %>% layout(xaxis = list(title = "Year"), 
                   yaxis = list(title = 
                "Oil Consumption per capita (tonnes per year)"))
```

## Oil consumption per capita by country

```{r, echo=FALSE}
setwd("C:/Users/Mikhail/Documents/Coursera/Data products")
oil <- read.xlsx(file = "Oil Consumption per capita.xlsx", sheetIndex = 1)
# leaving rows without NAs
oil_compl <- oil[complete.cases(oil),]
# renaming columns
names(oil_compl)[1] <- "country"
names(oil_compl)[2:47] <- 1965:2010
# "gathering", i.e. transforming the dataset so that year numbers are values in the year column
oil2 <- gather(oil_compl, key = year, value = oil.consumption, -country) 
oil2$year <- as.numeric(oil2$year)
#calculating averages

oil_country <- subset(oil2, (country == "China") | (country == "United States") | (country == "Germany") | (country == "Norway") | (country == "Venezuela"))
oil_country$country <- droplevels(oil_country$country)
plot_ly(data = oil_country, x = ~year, y = ~oil.consumption,  type = "scatter", mode = "lines+markers", color = ~country) %>% layout(xaxis = list(title = "Year"), yaxis = list(title = "Oil Consumption per capita (tonnes per year)"))
```

## That's it!
